Achieving maximum possible precision on stellar radial-velocity measurements in multi-epoch spectroscopy

### 2017-12-17 paper/paper.tex
disc para

...insert here one paragraph for each major result from the
abstract. Each paragraph should emphasize the awesome of the result,
but then discuss limitations or interpretation...

>>>>

Fundamentally, what we have shown is that a data-driven model for
stellar spectra can be accurate enough to deliver
radial-velocity (\RV) measurements that saturate information-theoretic
bounds.
It is not surprising that an accurate model of a stellar spectrum
yields good cross-correlation \RV\ measurements.
What is interesting (at least to us) is that there is sufficient
spectral information in a typical exoplanet-related \RV\ observing
program to determine the mean stellar spectrum to sufficient
quality that the \RV\ measurements are close to the best that can
theoretically be made.
It means that the information in the data that goes into determining
the mean stellar spectrum does not come at the expense (in any sense)
of the \RV\ information.

...insert here one paragraph for each of the other major results from
the abstract. Each paragraph should emphasize the awesome of the
result, and/or discuss limitations or interpretation...
